The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics [@Lesmerises_2018] that display temporal
[@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
social networks. In winter, caribou dig holes in the snow, termed craters, to
access forage [@Bergerud_1974]. As a result, caribou tend to occupy and re-use
craters once they are established and there is considerably less access to
forage than when the landscape is snow-free. Importantly, craters exist on the
landscape at multiple scales: the crater scale (a single crater), the feeding
area scale (multiple craters in close proximity), and the winter range scale
(all craters within an individual’s range) [@Mayor_2009]. The distribution of
forage for caribou is therefore seasonally heterogeneous, with greater access in
snow-free seasons compared to winter as well as spatially heterogeneous in
winter because the distribution of craters on the landscape varies meaning that
access to vegetation in winter is highly variable for caribou. We therefore
partitioned data into two discrete seasons: summer (3 August - 20 September) and
winter (1 January – 17 February) based on caribou socioecology [@Peignier_2019].

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@Bjørneraas_2010]. We did not collar all female caribou in the herd; however,
we assumed that our sample of collared animals was random.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 10 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
represents fine-scale decision making for caribou during foraging (Webber et al.
unpublished data), while re-sampling at 500 m and 1000 m represents the scale at
which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).

>>>>

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics [@Lesmerises_2018] that display temporal and spatial
variation in social networks [@Peignier_2019]. In winter, caribou dig holes in
the snow, termed craters, to access forage [@Bergerud_1974]. As a result,
caribou tend to occupy and re-use craters once they are established and there is
considerably less access to forage than when the landscape is snow-free.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
heterogeneous, with greater access in snow-free seasons compared to winter as
well as spatially heterogeneous in winter because the distribution of craters on
the landscape varies meaning that access to vegetation in winter is highly
variable for caribou. We therefore partitioned data into two discrete seasons:
summer (3 August - 20 September) and winter (1 January – 17 February) based on
caribou socioecology [@Peignier_2019].

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@BJ_RNERAAS_2010]. We did not collar all female caribou in the herd; however,
we assumed that our sample of collared animals was random.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 10 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).
